Time Series Bootstrapping For Solar Current

### 2021-12-15 deliverables/paper.Rmd
Confidence interval paragraph

>>>>

A percentile bootstrap confidence interval was calculated for both the dependent and *iid* estimates. This method was chosen for its simplicity and for the fact that the bootstrapped sampling distributions agreed with the assumption of normality under central limit theorem. Performing an *iid* bootstrap on dependent data should yield an artificially narrow confidence interval and this belief was supported by the relative widths of the resulting intervals.
